---
title: "hw1_B06208002"
author: "CARTUS YOU游博翔"
date: "2018年9月18日"
output: html_document
---

## 3.1 Calculator
```{r}
((2018-2017)/(2018-1998))*100
```
***

## 3.2 Workspace
```{r}
a <- 2018-2017
b <- 2018-1998
c <- a/b
p <- c*100
p
```
***

## 3.4 Functions
```{r}
v <- c(4,5,8,11)
sum(v)
```
***

## 3.5 Plots
```{r}
x <- rnorm(100)
plot(x)
```
***

## 4 Help and documentation
```{r}
help(sqrt)
```
***

## 5 Scripts
```{r}
source("firstscript.R")
source("firstscript.R")
source("firstscript.R")
```
***

## 6.2 Matrices
```{r}
P <- seq(from=31, to=60, by=1)
Q <- matrix(data=P, ncol=5)
Q
```
***

## 6.3 Data frames
```{r}
source('x123.R')
t <- data.frame(a=x1, b=x1+x2, c=x1+x2+x3)
plot(t)
source('x123.R')
t <- data.frame(a=x1, b=x1+x2, c=x1+x2+x3)
plot(t)
source('x123.R')
t <- data.frame(a=x1, b=x1+x2, c=x1+x2+x3)
plot(t)
```
***

## 7 Graphics
```{r}
plot(t$a, type="l", ylim=range(t), lwd=3, col=rgb(1,0.2,0,0.5))
lines(t$b, type="s", lwd=2, col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4, col=rgb(0,0.5,0.8,0.5))
```

arguments | Usage
----------|-----------------------------------------
    rgb   | control the color and transparency of the plot
    lwd   | control the line width
    pch   | specifies the type of points
    cex   | a numerical vector giving the amount by which plotting text and symbols.
    
***

## 8 Reading and writing data files
```{r}
d <- data.frame(a = c(1,2,4,8,16,32), g = c(2,4,8,16,32,64), x = c(3,6,12,24,48,96))
write.table(d, file="tst1.txt", row.names=FALSE)
d2 <- read.table(file="tst1.txt", header=TRUE)
d2$g <- d2$g*5
write.table(d2, file="tst2.txt", row.names=FALSE)
```
***

## 9 Not available data
```{r}
suppressWarnings(x <- sqrt(rnorm(100)))
mean(x, na.rm=TRUE)
```
***

## 10.2 Dates
```{r}
x_axis <- strptime(c('20180919000000', '20181205000000', '20190910000000'), format="%Y%m%d%H%M%S")
y_axis <- c(7,8,9)
plot(x=x_axis, y=y_axis)
```

***

## 11.2 For-loop
```{r}
h <- seq(from=1, to=100, by=1)
s <- c()
for(i in 1:100){
  if(i < 5 || i >90){
    s[i] = h[i]*10
  }
  else{
    s[i] = h[i]*0.1
  }
}
s
```
***

## 11.3 Writing your own functions
```{r}
myfun <- function(h){
  s <- c()
  for(i in 1:100){
    if(i < 5 || i >90){
      s[i] = h[i]*10
      }
    else{
      s[i] = h[i]*0.1
    }
  }
  return(s)
}
h <- rnorm(100)
myfun(h)
```
















